\subsection{Analysis by Experience}
% see Section 7.3 of \url{https://ieeexplore.ieee.org/abstract/document/8658125}

We highlight the results of our survey's closed questions by the reported professional experiences of the survey respondents in Tables \ref{table:analysis_by_experience_part1} and \ref{table:analysis_by_experience_part2}. The similar principles discussed in Section~\ref{analyze_by_professions} are applied for this report.

\input{Tables/analysis_by_experience_part1}
\input{Tables/analysis_by_experience_part2}

With the increase of professional experience, we see the percentage of software developer being decreased but manager being increased according to Q5 in Table~\ref{table:analysis_by_experience_part1}. On top of that, from Q7, we see to gather requirements of a software project, employees up-to mid-senior level, most of whom are developers, tend to use plain text, where more than 5 years experienced professionals prefer storyboard.

From the Q8 in Table~\ref{table:analysis_by_experience_part1}, we see implementation among all other development activities being the main concern for all levels of experienced employees. But interestingly, the ratio of the top two activities points out that the more senior an employee is, the more he/she tends to analyze the requirements of a software project.

As per the Q10 in Table~\ref{table:analysis_by_experience_part1}, we find that at the initial stage of career, professionals are inclined to prefer Windows most and then they mostly use Linux in mid-career and gradually they tend to use macOS at late-career. It might indicate that employees were proficient in Windows most before the start of their career. In Q5 of as per the Q10 in Table~\ref{table:analysis_by_experience_part1}, we see the percentage of developer up-to mid-career is the most and in late-career, the percentage of managers is noticeable which point out that developers are inclined to use Windows and Linux, and managers prefer macOS for their managerial tasks.

When participants were asked about their software testing practices, most of them per experience level were concerned about the unit and functional testing, pictured in Q14 of Table~\ref{table:analysis_by_experience_part2}. Moreover, we have found that senior participants are more prone to making software products accepted among clients using user acceptance testing (UAT). However, if we looked at Q15 when asked to level the automatic testing of their projects, the percentage is gradually decreasing with the seniority level like the ratio of the development activities of implementation and requirement analysis discussed earlier in this section. And most of the more than ten years of experience participants leveled test automation `2' for their projects. It implies that when it's time for testing practices like user acceptance testing rather than unit and functional testing, software industries are less likely to use test automation tools in their projects.
\boxtext{Testing practices like unit testing, functional testing, etc., used for implementation purposes, are mainly carried out as test automation in Bangladesh. But, for other testing practices like user acceptance testing, software companies tend not to carry out test automation tools more often.}

At Q17 of Table \ref{table:analysis_by_experience_part2} we observe that using tools for continuous deployment is commensurate to the years of professional experience. Personnel of senior-level are more likely to work in development and operations (DevOps) related fields.