\section{Implications of Findings}\label{implications}
The findings from our study can guide the following major stakeholders in software engineering (SE): 
\begin{inparaenum}[(1)]
\item SE Tool Creators to develop usable and affordable automated testing framework that can be accessible to emerging countries,     
\item SE Researchers to compare and contrast software development practices in emerging countries with respect to region-specific and global trends,   
\item SE career enthusiasts who would like to participate in the high-growth software industries in the emerging countries,    
\item SE security and performance practitioners to develop techniques to better enforce such crucial non-functional requirements in software products in emerging countries, and  
\item SE Industry leaders to offer customized region-specific software products and to promote diversity irrespective of regions.   
\end{inparaenum} We discuss the implications below.
% what are the implications of findings? say for another emerging country or software professionals or companies like Microsoft, Google?

 

\bf{\ul{Tool Creators.}} We have found that rigorous testing practice
is not prevalent in Bangladesh. The difference in testing effort between the
established software industry (e.g., Canada) and Bangladesh is too high. The
scenario is also true for other developing countries like Pakistan. From our
study, software practitioners may have an idea of their standing in software QA
in testing. Similar to all emerging industries, security testing is less
prioritized in Bangladesh. From our comparison, developers may better understand
security testing and security practices in other countries. While these findings show a 
difference in the adoption of testing tools and non-functional measures 
between emerging and developed countries, the reasons could be multi-faceted. 
For example, one reason of the prevalence of less automated testing in emerging countries 
like Bangladesh is that most of the developed software products are web-based. This means 
that developers in Bangladesh need to test their GUI-based software product. 
Proper software testing tool support for GUI testing is in infancy compared to 
the testing of source code. Good GUI-based testing tools are also not 
free or open-source. This makes it hard for developers in emerging countries to 
learn and use GUI-based testing framework. Therefore, 
while unit testing is practiced widely in Bangladesh as like any other countries, 
the lack of automated testing is due to the nature of the software products 
they developers are entitled to work on and the availability of a good, usable, and affordable 
testing framework to support them. Therefore, SE tool creators may create a
user-friendly framework to implement automatic testing for different types of
testing to address this affordability issue. Alternatively, 
cheaper and/or more affordable versions of the industry standard automated testing framework 
can be offered to developers of emerging countries. Containerization technologies are a popular trend worldwide. However, the
practice of containerization technologies is too low. Automatic
deployment/release is another under-practiced area. Tool creators can investigate
the challenges to incorporate these technologies in an emerging SE industry like
Bangladesh and offer more affordable alternatives. This is important because a software 
product developed in an emerging country like Bangladesh is actually consumed mostly in the developed 
countries (e.g., via outsourcing). Therefore, anyone can suffer from any lingering faults in the developed software products.

% Moreover, we have
% shown the level of automatic testing in the Bangladesh SE industry. Automatic
% testing is directly related to productivity. Practitioners can increase their
% productivity by implementing automatic testing for their products. Similarly, we
% have observed the under-use of automatic deployment/CI-CD tools. Practitioners
% should focus more on this area to automate their product pipelines.
% 
% We have also found that testing has been given less priority in the industry though
% it is one of the key elements for ensuring software quality. Furthermore,
% automatic testing, which is crucial for the efficiency and productivity of the
% test team, is rarely used. An automatic testing framework for other types of
% testing (such as GUI testing) may increase automatic testing practice. The price
% of quality automated testing tools may cause a lack of their use as the software
% budget in developing countries is often limited. Researchers 

\bf{\ul{Researchers.}} In SE research, we need to be aware of the current trends in software development practices not only 
to guide our research along the trends but also to ensure that our research contributions are timely and effective to the current 
needs of the software industry. In research, we strive to achieve generalizability of our findings, because otherwise we 
run the risk of becoming too niche or specific that may not cater to a global audience. Our study results of 
software development practices in an emerging country like Bangladesh and the comparison of 
such practices against multiple countries worldwide show that development practices, tools, techniques all could 
vary across the countries. Therefore, it may not be always possible to observe or enforce 
similar development practices across the globe, even when certain practices may be perceived as superior to others. 
A major reason of the observed differences between the emerging 
countries and developed countries is that outsourcing is a still a major source of revenue 
for the software industries in emerging countries. This explains why product design and overall architecture design 
is not widely practised in the software industries of emerging countries. A major 
focus in software engineering research is to understand team cohesion and collaboration. Given 
the outsourcing nature of the works carried by the software companies in the emerging countries, 
we can expect that the developers in the companies need to adapt to constantly dynamic teams where some 
team members are local and some others are remote and temporary, e.g., members from a software company 
of a developed country that are engaged in the outsourcing work. It is important to understand 
the productivity of the developers in such dynamic environment, the 
challenges they face (e.g., lack of enough in-person communication due to remote work and time difference).
Such research can offer findings in the development new methodologies, tools and techniques to facilitate 
better communication and collaboration practices among the developers in the such teams. This can 
then also help the software companies in emerging countries to offer better support to the overall system 
design and planning. 

\bf{\ul{Career Enthusiasts.}} We have found that certain languages (e.g.,
Java, JavaScript, etc.) and frameworks (e.g., Spring, Django, ASP.NET) have
extensive use in the software industry of Bangladesh. This finding is not different from 
other emerging countries. Therefore, career enthusiasts who aspire for a software development profession in 
emerging countries may focus on mastering such skills. Universities can update
their curricula to meet industry demand. The students aspiring to join the
software industry must prepare themselves accordingly to be productive quickly.
We have also found less automated testing practices in the industry of
Bangladesh. This may be related to a lack of exposure to the testing framework.
Similar to Hussain et al.\citep{Hussain2020}, we also suggest including
testing-related courses into the curriculum of universities and introducing
relevant assignments to have hands-on experience on automated testing tools
right from the student level. The students in their academic projects should
also use container and other DevOps tools to bring some qualitative improvement
for the industry when they join there.

\bf{\ul{Security and Performance Practitioners.}} More than 9.5\% of our respondents
responded that they do not take any measures to mitigate the security risk. The
common reason for not taking any measures is (1) the product is an early stage
(2) the respondents' role does not require any product security measures. The
reason for not taking any security measures is different from North
America \citep{Assal2019}. The reasons are (1) there are no formal test plans,
(2) lack of knowledge regarding testing tools. Though respondents do not think
about product security initially, it is recommended \citep{Chandra2009,Azham2011}
to plan security tests and product security from the design phase.

Modern frameworks provide the basic security of the solution. Moreover, some
framework provides enhanced, focused, customized security through a plug-in or
add-on, e.g., spring-security, spring-cloud security. Framework-based security
is a growing practice in the software industry\citep{Alssir2012}. The practice
in the Bangladesh SE industry matches the global practice. According to our
survey, it is the second most popular measure to mitigate security risk. Survey
respondents have reported using OWASP, HDIV, and spring security. Srinivasan et
al.\citep{Srinivasan2017} have conducted a comparison among the popular web
frameworks based on security. Based on five criteria, they ranked the
frameworks, and all of the mentioned frameworks of our respondents are in the
top 10 list. It seems that secure software engineering practice is prevalent in
the Bangladesh SE industry.


On a survey of 237 software professionals, Elahi et al.\citep{Elahi2011} found
that 51\% of respondents maintain at least one security standard, and 19\% of
respondents maintain ISO 17799 security standard. On the contrary, about 29.63\%
of respondents of the Bangladesh software industry maintain any security
standard. It is clear that security standards are not that much popular in this
SE industry.

According to Smith et al.\citep{Smith2003}, efficient architecture and
continuous monitoring tools are two of the twenty-four best practices to ensure
software performance. The respondents report both practices. However, Smith et
al. presented twenty-one other best practices, and we have not found other
practices in our survey. It is clear the SE industry of Bangladesh only
practices a few best measures for ensuring software performance.

% 27.1\% of respondents in our survey reported that they use the load balancer
% to ensure software performance. A load balancer is mostly used to reduce queue
% time/ response time in web base application\citep{Mesbahi2016}. Thus we can
% infer that most of our survey respondents mainly engaged in developing the
% web-based application.


Bondi et al.\citep{Bondi2000} have listed four scalability types to ensure
software capability to scale; however, we observe only one scalability type
(load scalability) in our responses. To obtain software scalability use of cloud
services is one of the most popular strategies\citep{Gao2011}. Another popular
strategy is the use of microservice. Microservice and cloud services together
allow the user to scale up and down any system dynamically. C\'{a}ceres et
al.\citep{Cceres2010} reported that cloud services and microservice-based
architecture are generally used together to ensure scalability. In the
Bangladesh SE industry, this practice may be prevalent. The use of cloud service
and efficient use of architecture are the second and third most popular topic
among our respondents.

Overall, the findings show that much need to be done to ensure proper security and performance measures 
in the software development practices of emerging countries. Multi-faceted efforts are warranted like 
development of affordable tools and techniques for the emerging countries, enforcement of widely-accepted and 
measurable industry standards across the regions, and the proper training of the security and performance 
principles to the developers in emerging countries. 

\bf{\ul{Industry Leaders.}} This study found that the Bangladesh software
industry lags in adopting some of the current industry trends. Bangladesh can be
a good marketplace for cloud companies like Microsoft, Google, and Amazon if
they provide an affordable package for the software companies operating here.
Local entrepreneurs may also think of building cost-effective local public
clouds along with providing some common DevOps services.

Moreover, we have found most of the participants in our study are engaged in web
technology. This may indicate that the web is the most popular form among users
of Bangladesh. This observation can help the industry owners to select
appropriate medium while targeting users of this region. %We have identified
common practices of the practitioners of the Bangladesh software industry.

Finally, we have identified that the
participation of female in the Bangladesh SE industry is comparatively less than
that of male engineers (see Section \ref{analysis by gender}). Hussain et al.\citep{Hussain2020} expressed a
concern that there may be bias in the hiring process of the industry. Overall, the under-representation of 
females and minorities in software industries worldwide is a prevalent and ongoing concern. 
This was also reported in the 2020 Stack Overflow developer survey, where more than 90\% respondents 
were males. Our findings confirm similar trends in Bangladesh. Therefore, proper measures 
need to be taken to encourage equity, diversity, and inclusion in software industries across the regions.  
Such measures may be better enforced by tailoring the measures to region-specific cultural attributes.
%Further
%research may be conducted to identify the inherent reason behind these facts.

