\subsection{Analysis by Professions}
\label{analyze_by_professions}
% summarize key findings by professions. see Section 7.2 of \url{https://ieeexplore.ieee.org/abstract/document/8658125}
In Tables \ref{table:analysis by profession part1}, \ref{table:analysis by profession part2}, and \ref{table:analysis by profession part3}, we summarize the interesting results of our survey's closed questions by survey participants' reported roles. For all questions, we reported the top values for each role. For example, for the question ‘Which of the following do you use for requirements gathering?’ in Table \ref{table:analysis by profession part1}, we reported Plain Text for the developer's role. 26.2\% of software engineers use plain text for requirement gathering. Of all the other processes used by developers, the most commonly used requirement gathering process is plain text.

% \begin{enumerate}[label=\arabic*)]
%   \item Multiple Choice Questions. If the question has two options (Male, Female), we only show the result of the option(s) with the majority agreement.
%   \item For all other questions, we reported the top two values for each role. For example, for the question ‘Which of the following do you use for requirements gathering?’ in Table \ref{table:analysis by profession part1}, we reported PT (Plain Text) and SB (Story Board) for the software engineer's role. 26.2\% of software engineers use PT, and 22.99\% use SB. These two requirements gathering processes are the top two among all the other processes used by software engineers.
% \end{enumerate}

\input{Tables/Analysis_by_Profession_Part1}
\input{Tables/Analysis_by_Profession_Part2}
\input{Tables/Analysis_by_Profession_Part3}
The agile method is the most practiced software requirement method in Bangladesh. It is popular among respondents of almost all positions. The second popular method is Scrum.
\boxtext{Agile is the most practiced requirement gathering method. The popularity of the Agile method is consistent across the different reported roles in our surveys.}

In Q8, participants were asked to identify the SDLC activity, where most of the time is spent. Generally, it is expected that participants in the senior role (e.g., manager, team lead) will spend time in requirement analysis, documentation where participants in the junior role (e.g., developers, r\&d engineer) will spend time in implementation and testing. From Q8 in Table \ref{table:analysis by profession part1}, we observe that senior role participants mostly spend time in requirement analysis and documentation. However, testing is not in the top three most times spent activity. For participants in the junior role, the most time-consuming activity is implementation, and the second-most time-consuming activity includes several other SDLC steps (e.g., maintenance, requirement analysis, etc.). This may indicate that in Bangladesh, SE industry testing is considered comparatively less important.
\boxtext{Across all roles, implementation is the most time spent activity in SDLC. However, testing is not considered one of the most time-consuming activities. Rigorous testing practices may not be prevalent in the Bangladesh SE industry.}
In most of the roles, Java is the most used languages (Java is the second most used language in cases where JavaScript is the most used language). Even in the data engineer role, Java is the most used language, though Python is mostly used in data processing. Like Java, Spring (one framework of Java) is the widely used framework regardless of role.
\boxtext{Java and JavaScript are the most used languages regardless of role.}
From Q15 of Table \ref{table:analysis by profession part3}, we observe that developers mostly practice the highest automated testing level. In Q13 of Table \ref{table:analysis by profession part3} shows that developers mostly practice unit testing. It is comparatively easier to achieve automated testing through unit testing because of several testing frameworks. This may be one of the reasons behind the high level of automated testing among developers. Automated tests offering libraries/frameworks for other types of testing can encourage higher automated testing levels in other roles.
\boxtext{Developers mostly practice the highest level of automated testing. Automated testing frameworks for other types of testings may increase the practice of automated testing.}