\subsubsection{Software testing and devops practices used (D3)}\label{sec:rq2-d3}
\input{Tables/testing_comparison}We compare the observations from three questions in our survey: \begin{inparaenum}
\item Software Testing Practices (Q14),
\item Level of Automated Testing (Q15),
%\item Tools Used in Testing and QA (Q16),
%\item Continuous Deployment tools (Q17), and
%\item Version Control (Q18).
\end{inparaenum} We summarize the comparisons in Table \ref{table:testing_comparison} and discuss those below.
%To get the picture of quality assurance (QA) in countries such as Malaysia, Turkey, France, etc., different studies have been carried out. In Table \ref{table:testing_comparison}, we compare the major outcomes of testing and deployment related responses from our study with the similar results of the previous studies. The comparative picture is discussed below.

% \begin{itemize}
%     % \item Requirements Clarity
%     \item Software Testing Practices (Q14)
%     \item Level of Automated Testing (Q15)
% \end{itemize}

%\paragraph{Software Testing Practices}
\nd\bf{$\bullet$ Software Testing Practices (Q14)}. From our study, as per
\ref{fig:testing}, we see an interesting point that unit testing (53\%) and
functional testing (49\%) are moderately used in Bangladesh, whereas from
\citep{Garousi2013} and \citep{Wang2018} we can see that relatively a high
percentage of their survey respondents in both Canada New Zealand rely on unit
testing with 79.27\% and 73\% respectively. On the other hand, the adoption of
acceptance testing and UI testing is quite similar to these countries. In
Malaysia, based on \citep{Baharom2006}, Baharom et al. reported that, according
to their survey, unit testing (68.29\%), integration testing (78.05\%), system
testing (85.37\%), and acceptance testing (78.05\%) are used by most
organizations in a high percentage, and about half of the organizations are
carrying out alpha and beta testing.

%\boxtext{Software developers around the world usually give unit testing the top priority, but the developers in Bangladesh have comparatively less participation.}
%\rifat{Is the above observation correct? 53\% usage of unit testing reported.}\khalid{added percentages. The response rate of unit testing in our survey lags compares to others. Is it okay now?}

%\paragraph{Level of Automated Testing}
\nd\bf{$\bullet$ Level of Automated Testing (Q15).} We have found that as per
\ref{fig:autoTest}, around 25\% of our respondents are highly concerned that
they have to use automated testing for their projects, while around 35\% of our
respondents have expressed medium level concern and the remaining are hardly
concerned about using automated testing. From the study of Dutta et al.
\citep{dutta1999}, we have found that in automated testing practices, Bangladesh
is quite similar to all of Europe but lags behind France. According to their
study, the usage rate of automation testing tools in overall Europe is 26\%,
where in France, it is as high as 61\%. But in Israel, this rate is the only
9\%.

\begin{tcolorbox}[flushleft upper,boxrule=1pt,arc=0pt,left=0pt,right=0pt,top=0pt,bottom=0pt,colback=white,after=\ignorespacesafterend\par\noindent]
\nd\it{\bf{RQ2-D3. Software testing and devops practices used.}} 
In the adoption of test automation and widespread unit testing, the Bangladesh SE industry lags behind developed countries'  SE industry. 
Software developers around the world usually give unit testing the top priority, but the developers in Bangladesh have comparatively less participation. %\gias{summarize}
%\partha{Added}
\end{tcolorbox}
