\section{Study Results}
\label{study_results}
We answer two research questions by analyzing of our survey responses and by comparing our results against surveys conducted for other countries:
\begin{enumerate}[label=RQ\arabic{*}., leftmargin=26pt]
  \item What are the software development practices in an emerging country like Bangladesh? (Section \ref{RQ1})
  \item How do the development practices in Bangladesh differ from other developed countries? (Section \ref{RQ2})
\end{enumerate}
% \section{Study Results}
% \subsection{Development Practices and Processes in Bangladesh (RQ1)}
% We divide this into four sub-questions:
% \begin{enumerate}
%     \item What software methodology are used in your project?
%     \item Which implementation technologies and tools are adopted by software
% development professionals?
% \item  What type of testing and deployment practices are used?
% \item How are the security and performance is ensured in a product of a company?
% \end{enumerate}
% \subsection{Comparison among countries (RQ2)}
% We do the comparison along the following dimensions:
% \begin{enumerate}
%     \item Development methods and practices
%     \item Implementation technologies
%     \item Quality assurance
%     \item Release and iterations
% \end{enumerate}

%We have explored two research questions in this study. 
The first research question focuses on the dimensions of software development
practices and processes in Bangladesh. The second research question compares those
practices prevailing in Bangladesh with other regions to reveal the similarities
and dissimilarities in software development practices and processes.

\subsection{Development Practices and Processes in Bangladesh (RQ1)}
\label{RQ1}
Following previous studies in region-based software development process analysis~\citep{Garousi2013, Garousi2015, Vonken2012, Wang2018}, we 
analyze the development practices and processes in Bangladesh along four dimensions (D):
\begin{enumerate}[label=D\arabic{*}., leftmargin=20pt]
  \item Software development methodologies used (Section \ref{methodology}). We investigate the development
processes, methodologies, requirements analysis processes.
  \item Software tools and techniques used (Section \ref{tools}). We determine the
trending technologies like platforms, programming languages, and frameworks.
\item Software testing and devops practices used (Section \ref{testing_practices}). We explore the
present situation of testing and deployment practices.
\item Security and performance measures used (Section \ref{security_performance}). We analyze how
software companies secure and maintain their code and what practices are
followed to ensure performance and scalability.
\end{enumerate}
%We divide this into the following four sub-questions which explore software development practices and processes in Bangladesh in more detail.

\input{RQ1_Methodology}
\input{RQ1_Technology_and_Tools}
\input{RQ1_Testing_and_Deployment}
\input{RQ1_Security_Performance_Scalability}

\subsection{Comparison of Development Practices Among Countries (RQ2)}
\label{RQ2}

This section presents a comparative discussion on different dimensions of software development practices and processes among different regions of the world along with Bangladesh. We make the comparison along the following dimensions:

\begin{itemize}
\item Development methods and practices
\item Implementation technologies
\item Quality assurance
\item Release and iterations
\end{itemize}

The following subsections describe these dimensions.

\input{RQ2_Developemnet_Practices}
\input{RQ2_Technology}
\input{RQ2_QA}
% \input{Sections/Study_Results_Part/RQ2_VCS}
\input{RQ2_Security_Performance_Scalability_Comparison}




% \input{Sections/study_results_RQ1}
% \input{Sections/study_results_RQ2}
