\section{Implications of Findings}

% what are the implications of findings? say for another emerging country or software professionals or companies like Microsoft, Google?

\label{implications}
Thus far, we have discussed the SE practices of Bangladesh and also their similarities/dissimilarities with both established and emerging SE industries. In this section, we discuss the implications of our findings. Apart from helping the researchers to understand SE challenges in the emerging software industry, our study can also help industry leaders, software practitioners, universities, and open source development projects.

\indent \textbf{Researchers:} In this study, we have identified that the participation of female in the Bangladesh SE industry is comparatively less than that of male engineers. \anindya{From which part of the study you found this? No RQ has any result on it as far as I remember.}\partha{updated}\partha{Based on section \ref{analysis by gender}} Hussain et al.\cite{Hussain2020} expressed a concern that there may be bias in the hiring process of the industry. Also, it appears that nowadays females are less interested in joining the software industry\anindya{Any supporting response? Otherwise, too speculative comment.}. Further research may be conducted to identify the inherent reason behind these facts. We have also found that testing has been given less priority in the industry though it is one of the key elements for ensuring quality of a software. Furthermore, automatic testing, which is crucial for efficiency and productivity of the test team, is rarely used. An automatic testing framework for other types of testing (such as GUI testing) may increase automatic testing practice.  The price of quality automated testing tools may be a cause of lack of their use as the software budget in developing countries is often limited. Researchers may work to create a user-friendly framework to implement automatic testing for different types of testing to address this affordability issue. This finding may encourage researchers develop open source tools for the industry of developing countries. 

We have found that certain development methods are popular with a particular group (agile in females). Further study may be conducted to investigate the problems associated with incorporating other development methods in those groups. \anindya{Development methods are determined by the technical management of a company. Correlating it with the female/male respondent is not a practical idea I think. This point may be omitted.}

Containerization technologies are a popular trend worldwide. However, the practice of containerization technologies is too low. Automatic deployment/release is another under-practiced area. Researchers can investigate the challenges to incorporate these technology in an emerging SE industry like Bangladesh.

\indent \textbf{Software Practitioners:}  We have found that rigorous testing practice is not prevalent in Bangladesh. The difference in testing effort between established software industry (e.g., Canada) and Bangladesh is too high. The scenario is also true for other developing countries like Pakistan. From our study, software practitioners may have an idea of their standing in software QA in terms of testing. Similar to all emerging industries, security testing is less prioritized in Bangladesh. From our comparison, developers may better understand security testing and security practices in other countries. Moreover, we have shown the level of automatic testing in the Bangladesh SE industry. Automatic testing is directly related to productivity. Practitioners can increase their productivity by implementing automatic testing for their products. \anindya {Can we also write: Similarly automatic deployment and CI/CD also need more focus as their under-practice is revealed in the survey}.

\indent \textbf{Universities:} We have found that certain languages (e.g., Java, Javascript, etc.) and frameworks (e.g., Spring, Django, ASP.NET) have extensive use in the software industry of Bangladesh. Universities can update their curricula to meet industry demand. The students aspiring to join software industry must prepare themselves accordingly to be productive in a very short period. We have also found less automated testing practice in the industry of Bangladesh. This may be related to a lack of exposure towards the testing framework. Similar to  Hussain et al.\cite{Hussain2020}, we also suggest including testing-related courses into the curriculum of universities and introducing relevant assignments to have hands-on experience on automated testing tools right from the student level. Container and other DevOps tools also should be used by the students in their academic projects so that they can bring some qualitative improvement for the industry when they join there.


\indent \textbf{Industry Leaders:} This study found that the Bangladesh software industry lags in adopting some of the current industry trends. Bangladesh can be a good marketplace for cloud companies like Microsoft, Google, and Amazon if they provide affordable package for the software companies operating here. Local entrepreneurs may also think of building cost-effective local public clouds along with providing some common DevOps services.   

Moreover, we have found most of the participants in our study are engaged in web technology. This may indicate that the web is the most popular form among users of Bangladesh. This observation can help the industry owners to select appropriate medium while targeting users of this region. %We have identified common practices of the practitioners of the Bangladesh software industry.


\indent \textbf{Emerging Software Industries:} We have identified some practices in Bangladesh, which are also applicable to other emerging software industries. We have seen that testing is given less priority in the emerging industry than in the established industry. Rigorous testing practices can help these industries be at par with others in global competition.
\anindya{This point of Emerging Software Industries does not carry an implication worth discussion. May be omitted unless more meaningful insight is offered.}
